A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Beam Dynamics

### 2018-04-10 paper/theor-experiment.tex
starting plots for paper

\subsubsection{AWA Optimization Results}
Given the parameters and variable boundaries in Section \ref{awaproblem}, 
four 50 generation optimization experiments were done with varying GA parameters. 
Similar to the time step scan, the goal was to determine which set of optimization
parameters strongly influence the results, and whether there was a time to solution
difference. (NOTE FOR EDIT: May need to take this out, or compare at 50 generations, none of these runs finished 100 gens)

>>>>

\subsubsection{AWA Optimization Results}
Given the parameters and variable boundaries in Section \ref{awaproblem}, 
four optimization experiments were done with varying GA parameters, see Table \ref{extable}.
From here on, we will reference each experiment as ex-1, ex-2, ex-3 and ex-4. 
They were each allowed to run for twenty four hours. 
Similar to the time step scan, the goal of this exercise was to determine which set of optimization
parameters strongly influence the results, and whether there was a time to solution
difference.

\begin{table}%[h!]
	\begin{center}
		\caption{Input Parameters for initial twenty four hour AWA optimization experiments. 
			The gene mutation probability was equal to the mutation probability (not shown) in all four experiments.}
		\label{extable}
		\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} C C D }
			\hline\noalign{\smallskip}
			& Gene Mutation Probability & Recombination Probibility & Number of completed generations \\
			\noalign{\smallskip}\hline\noalign{\smallskip}
			ex-1 &  0.1  & 0.9  &  96 \\
			ex-2 &  0.3  & 0.7  &  81 \\
			ex-3 &  0.8  & 0.2  &  53 \\
			ex-4 &  0.01 & 0.09 &  95 \\
			\noalign{\smallskip}\hline
		\end{tabular*}
	\end{center}
\end{table}

After collection of all data, the Pareto front of each data set was plotted.
